### 2021-02-26 paper/fse21/eval.tex
Fix typos
Run spell checker

To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost (Comm. Cost) between analyzers and the number of dynamic shortcuts.
For 199 original tests, Comm. Cost was only
1.58\% compared to the analysis time of no-DS.  However, for 156
abstracted tests, Comm. Cost was 31.06\% compared to the analysis
time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for 156 abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time of
no-DS and the $y$-axis denotes the number of dynamic
shortcuts and the number of corresponding tests.
For all 156 tests, Comm. Cost is larger than
both the static analysis time (Static) and the dynamic analysis
time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
Comm. Cost is modest compared with the baseline static
analysis time.  However, the more dynamic shortcuts are performed,
the less the performance benefits by using dynamic shortcuts.
Specifically, when dynamic shortcuts are performed more than 20 times,
Comm. Cost is even larger than half of cost of no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing Comm. Cost between
the static analyzer and the dynamic analyzer.

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of failed assertions produced by no-DS and DS, respectively;
each circle denotes each test in the heatmap form. The darker the circle is, the more tests it indicates.
The top line
denotes the y=x line, and the bottom solid line denotes the average improvement.
For 199 original tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
completely removed the failed assertions for 24 tests, reducing the nuber of failed assertions by 92.79\% on average.
For 156 abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
the number of failed asserions by 12.31\% on average.
Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions
for original and abstracted tests, respectively.

>>>>

To experimentally evaluate the conjecture, we investigated the relationship between
the communication cost (Comm. Cost) between analyzers and the number of dynamic shortcuts.
For 199 original tests, Comm. Cost was only
1.58\% compared to the analysis time of no-DS.  However, for 156
abstracted tests, Comm. Cost was 31.06\% compared to the analysis
time of no-DS.  Figure~\ref{fig:abs-analysis-ratio} presents the
analysis time ratio for 156 abstracted tests.
The $x$-axis represents the time ratio normalized by the total analysis time of
no-DS and the $y$-axis denotes the number of dynamic
shortcuts and the number of corresponding tests.
For all 156 tests, Comm. Cost is larger than
both the static analysis time (Static) and the dynamic analysis
time (Dynamic).  When dynamic shortcuts are performed less than 10 times,
Comm. Cost is modest compared to the baseline static
analysis time.  However, the more dynamic shortcuts are performed,
the less the performance benefits by using dynamic shortcuts.
Specifically, when dynamic shortcuts are performed more than 30 times,
Comm. Cost is even larger than half of cost of no-DS.
Based on this evaluation result, we believe that we can leverage
dynamic shortcuts by optimizing Comm. Cost between
the static analyzer and the dynamic analyzer.

@@

Figure~\ref{fig:precision} depicts the comparison of the analysis
precision between no-DS and DS.  The $x$-axis and the $y$-axis denote
the number of failed assertions produced by no-DS and DS, respectively;
each circle denotes each test in the heat-map form. The darker the circle is, the more tests it indicates.
The top line
denotes the y=x line, and the bottom solid line denotes the average improvement.
For 199 original tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(a) shows that dynamic shortcuts
completely removed the failed assertions for 24 tests, reducing the number of failed assertions by 92.79\% on average.
For 156 abstracted tests that are analyzable by both analyzers,
Figure~\ref{fig:precision}(b) shows that dynamic shortcuts successfully cut down
the number of failed assertions by 12.31\% on average.
Thus, on average, dynamic shortcuts removed analysis of 92.79\% and 12.31\% failed assertions
for original and abstracted tests, respectively.
